---
title: "Project"
author: "Tejas"
date: "6 April 2019"
output:
  pdf_document: default
  html_document: default
---
#Importing Libraries
```{r}
library(igraph)
library(centiserve)
library(ggplot2)
library(meaRtools)
library(roots)
library(MetaIntegrator)

```
#Reading C. Elegans Worm Data
```{r}
celegans_other<- read.csv("C:/Users/Tejas/Documents/celegans_n306.txt", 
                          header = F, sep = " ", dec = " ")
names(celegans_other) <- c("Sample.Name", "Marker", "Size")
G <- graph.data.frame(celegans_other)
```



```{r}
plot(degree.distribution(G), pch=20, cex=1, col="brown", 
     xlab="node degree ",
ylab = "probability ", 
main = "Degree distribution of C. elegans Neural Network")
lines(degree_distribution(G))
```

#Degree of Nodes
```{r}
G.degrees <- degree(G)
print(G.degrees)
```

```{r}

clust<- transitivity(G, type="weighted")
plot(clust, pch=20, cex=1, col="blue", 
     xlab="No. of Nodes ",
ylab = "Clistering Coefficient ", 
main = "C. ELegans Clustering Coefficient Distribution", type="b")
lines(clust)
```

#List of Cores

```{r}
cores = coreness(G)
print(cores)
```


```{r}
plot(cores, col="blue", xlab="Nodes",ylab = "Cores ",
     main = "C.Elegans Worm K-Core Distribution", type = "h")
lines(cores)
```




```{r}
CorenessLayout <- function(G) {
coreness <- graph.coreness(G);
xy <- array(NA, dim=c(length(coreness), 2));
 
shells <- sort(unique(coreness));
for(shell in shells) {
v <- 1 - ((shell-1) / max(shells));
nodes_in_shell <- sum(coreness==shell);
angles <- seq(0,360,(360/nodes_in_shell));
angles <- angles[-length(angles)]; # remove last element
xy[coreness==shell, 1] <- sin(angles) * v;
xy[coreness==shell, 2] <- cos(angles) * v;
}
return(xy);
}
 
# g is the network
# compute coreness
coreness <- graph.coreness(G);
# assign colors
colbar <- rainbow(max(coreness));
# create layout
ll <- CorenessLayout(G);
# plot
plot(G, layout=ll, vertex.size=20, 
     vertex.color=colbar[coreness], 
     vertex.frame.color=colbar[coreness], 
     main='C. Elegans Worm Coreness');
```
```{r}
plot(G, main = "Original C. Elegans Worm Network Visualization")
```

#Rewiring of Worm Network


```{r}
keeping_degseq(loops = FALSE, niter = 8000)
g <- G
g %>%
  rewire(keeping_degseq(niter = 8000)) %>%
  degree()

str(rewire(g, with = keeping_degseq(niter = vcount(g) * 10)))
plot
```
```{r}
plot(g, main="Rewired C. Elegans Network Visualization ")
```


#Reading Mouse brain Neural Network

```{r}
library(igraph)
mouse_raw<- read.csv("C:\\Users\\Tejas\\Documents\\bn-mouse_brain_1.edges", 
                     header = F, sep = " ", dec = " ")
mouse<-read.graph("C:\\Users\\Tejas\\Documents\\bn-mouse_brain_1.edges","edgelist")
mouse<- simplify(mouse, remove.multiple = TRUE, 
                 remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))
any(which_multiple(mouse))
E(mouse)$weight

is_simple(mouse)
```


```{r}


plot(degree.distribution(mouse), pch=20, cex=1, 
     col="green", xlab="node degree ",
ylab = "probability ", main = "Degree distribution of Mouse Brain Neural Network")
lines(degree_distribution(mouse))

```

# Degrees of Nodes

```{r}
mouse.degrees <- degree(G)
print(mouse.degrees)
```
#List of Cores
```{r}
cores_mouse = coreness(mouse)
print(cores_mouse)
```



```{r}
plot(cores_mouse, pch=2, cex=0.5, 
     col="red", xlab="Index",
ylab = "Cores ", main = "Mouse K-Core Distribution")
lines(cores_mouse)
```



```{r}
CorenessLayout <- function(mouse) {
coreness <- graph.coreness(mouse);
xy <- array(NA, dim=c(length(coreness), 2));
 
shells <- sort(unique(coreness));
for(shell in shells) {
v <- 1 - ((shell-1) / max(shells));
nodes_in_shell <- sum(coreness==shell);
angles <- seq(0,360,(360/nodes_in_shell));
angles <- angles[-length(angles)]; # remove last element
xy[coreness==shell, 1] <- sin(angles) * v;
xy[coreness==shell, 2] <- cos(angles) * v;
}
return(xy);
}
 
# g is the network
# compute coreness
coreness <- graph.coreness(mouse);
# assign colors
colbar <- rainbow(max(coreness));
# create layout
ll <- CorenessLayout(mouse);
# plot
plot(mouse, layout=ll, vertex.size=30, 
     vertex.color=colbar[coreness], 
     vertex.frame.color=colbar[coreness], main='Mouse Coreness');
```

```{r}
plot(mouse, main="Mouse Network Visualization Original")
```





#Rewiring Mouse Network



```{r}
keeping_degseq(loops = FALSE, niter = 8000)
mouse_dummy <- mouse
mouse_dummy %>%
  rewire(keeping_degseq(niter = 8000)) %>%
  degree()
str(rewire(g, with = keeping_degseq(niter = 
                                      vcount(mouse_dummy) * 10)))
```


```{r}
plot(mouse, main="Reqired Mouse Network Visualization")

```


```{r}
clust<- transitivity(mouse, type="weighted")
plot(clust, pch=20, cex=1, col="brown", xlab="No. of Nodes ",
ylab = "Clustering Coefficient ", 
main = "Mouse - Clustering Coefficient Distribution")
lines(clust)

```
#Strength Measure for Worm Network

```{r}
worm_strength<- strength(G, vids = V(G), mode = "all",
  loops = TRUE)
which.max(worm_strength)
```


```{r}
plot(worm_strength, ylab = "Strength", 
     xlab = "Node ID", 
     main = "C. Elegans Worm - Node Strength Plot", col= "red", type="h")
lines(worm_strength)
```

#Strength Measure for Mouse Network

```{r}
mouse_strength<- strength(mouse, 
                          vids = V(mouse), mode = "all",
  loops = TRUE)

mouse_strength
```



```{r}

plot(mouse_strength, ylab = "Strength", 
     xlab = "Node ID", main = "Mouse - Node Strength Plot", 
     col= "red", type="h")
lines(mouse_strength)
```


#Max-Flow

```{r}

g1 <- graph_from_data_frame(as.data.frame(celegans_other))

worm_maxflow<- max_flow(g1, source=V(g1)["1"], target=V(g1)["2"])
worm_maxflow
```

```{r}

plot(worm_maxflow$cut, xlab = "CUT - MaxFlow", 
     ylab = "Edges", main = "C. Elegans Worm Max-Flow Plot", 
     col= "brown", type="h")
lines(worm_maxflow$cut)
```




```{r}
worm_central<- centr_clo(G, 
                         mode = c("out", "in", "all", "total"), 
                         normalized = TRUE)
mean(worm_central$res)
```
```{r}

plot(worm_central$res, xlab = "Nodes", ylab = "Strength", 
     main = "C. Elegans Worm - Closeness Centrality", 
     col= "blue", type="b")
lines(worm_central$res)
```

#Page Rank Measure

```{r}
p<- page_rank(G, algo = c("prpack"), vids = V(G),
  directed = TRUE, damping = 0.85, 
  personalized = NULL, weights = NULL,
  options = NULL)
mean(p$vector)
#sort(p$vector, decreasing = TRUE)

```



```{r}

plot(p$vector, ylab = "Page Rank", 
     xlab = "Node ID", main = "C. Elegans Worm Page Rank Plot", 
     col= "red", type="b")
lines(p$vector)
```

#Betweenness Meaure


```{r}
worm_betweenness<- betweenness(G, v = V(G), 
                               directed = TRUE, weights = NULL,
                               nobigint = TRUE, normalized = FALSE)

plot(worm_betweenness, ylab = "Betweenness", xlab = "Node ID", 
     main = "C. Elegans Worm Betweenness Plot", col= "red", type="h")
lines(worm_betweenness)
sort(worm_betweenness, decreasing = TRUE)
```

```{r}
worm_closeness<- estimate_closeness(G, vids = V(G), 
                                    mode = c("in"), cutoff="0", 
                                    weights = NULL, 
                                    normalized = FALSE)

plot(worm_closeness, ylab = "Closeness", xlab = "Node ID", 
     main = "C. Elegans Worm Closeness Plot", col= "red", type="b")
lines(worm_closeness)
```


#Authority Score:

```{r}
worm_authority<- authority_score(G, scale = TRUE, weights = NULL,
  options = arpack_defaults)
mean(worm_authority$vector)
plot(worm_authority$vector, 
     ylab = "Authority Score", xlab = "Node ID", 
     main = "C. Elegans Worm Authority Score Plot", 
     col= "red", type="h")
lines(worm_authority$vector)
```
#Hub Score:


```{r}
worm_hub<- hub_score(G, scale = TRUE, 
                     weights = NULL, options = arpack_defaults)
mean(worm_hub)
plot(worm_hub$vector, ylab = "Hub Score", 
     xlab = "Node ID", 
     main = "C. Elegans Worm Hub Score", col= "red", type="h")
lines(worm_hub$vector)
```

#Modularity Score

```{r}
g <- G
wtc <- cluster_walktrap(g)
modularity(wtc)
modularity(g, membership(wtc))
```


```{r}
g1 <- graph_from_data_frame(as.data.frame(mouse_raw))

mouse_maxflow<- max_flow(g1, source=V(g1)["1"], 
                         target=V(g1)["2"])


plot(mouse_maxflow$cut, 
     ylab = "Edges", xlab = "Max-Flow", 
     main = "Mouse - Max Flow Plot", 
     col= "red", type="h")
lines(mouse_maxflow$cut)
```



```{r}
mouse_closeness<- estimate_closeness(mouse, vids = V(mouse), 
                                     mode = c("in"), cutoff="0", 
                                     weights = NULL, 
                                     normalized = FALSE)
mean(mouse_closeness)
plot(mouse_closeness, ylab = "Closeness measure", 
     xlab = "Node ID", main = "Mouse Closeness Plot", 
     col= "red", type="h")
lines(mouse_closeness)

```

```{r}
p<- page_rank(mouse, algo = c("prpack"), vids = V(mouse),
  directed = TRUE, damping = 0.85, personalized = NULL, weights = NULL,
  options = NULL)

sort(p$vector, decreasing = TRUE)
plot(p$vector, ylab = "Page Rank", 
     xlab = "Node ID", main = "Mouse - Page Rank Plot", 
     col= "red", type="h")
lines(p$vector)

```


```{r}
mouse_betwenness<- betweenness(mouse, v = V(mouse), 
                               directed = TRUE, weights = NULL,
  nobigint = TRUE, normalized = FALSE)

plot(mouse_betwenness, ylab = "Betweenness", 
     xlab = "Node ID", main = "Mouse Betweenness Plot", 
     col= "red", type="h")
lines(mouse_betwenness)
```

```{r}
mouse_authority<- authority_score(mouse, scale = TRUE, weights = NULL,
  options = arpack_defaults)
mean(mouse_authority$vector)
plot(mouse_authority$vector, 
     ylab = "Mouse Authority Score", xlab = "Node ID", 
     main = "Mouse Authority", col= "red", type="h")
lines(mouse_authority$vector)
```
```{r}
mouse_hub<- hub_score(mouse, scale = TRUE, 
                      weights = NULL, 
                      options = arpack_defaults)

plot(mouse_hub$vector, ylab = "Hub Score", 
     xlab = "Node ID", main = "Mouse Hub Score", 
     col= "red", type="h")
lines(mouse_hub$vector)
```
#Modularity:

```{r}
g <- mouse
wtc <- cluster_walktrap(g)
modularity(wtc)


```






